### 2019-03-07 manuscript/results.tex
- addition of a promised diploidization justification and fodder for discussion - requisite references - fixed spilled text on pathways table
various minor manuscript edits
pathways using proportion instead of ratio

When considering breeding system alone (I/C model, \cref{figure:netdivall}C), we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010}. %B: moved \cref{} earlier; avoids seeming related to \citep{}
When a hidden state is included (I/C+A/B model), the large net diversification difference persists for one of the hidden states but is removed for the other (\cref{figure:netdivall}D).
Thus, differences in net diversification are best explained by both breeding system and an unknown factor.
% The transition rate from SI to SC is $q_{IC}=0.3$ for both the I/C and the I/C+A/B models.
The statistical model comparison shows very strong support for including the hidden state (\cref{table:bayesfactors}).

@@

% E todo: could make this look a little less klunky
\begin{figure}
    \centering \includegraphics[width=0.9\textwidth]{pathways}
    \caption{
        %B: FIXME: R&E check this re-wording to see if it is to your liking--I think I clarified it a bit, although with length increase.
        %Contributions of the two pathways to polyploidy.
        %When considering only rates of transitions among the states (left), the one-step pathway dominates on short timescales and the two-step on long timescales.
        %When also considering diversification within each state (right), the one-step pathway dominates over any timescale.
        %The lower panels plot the ratio of the two pathway contributions in the upper panels.
        Contributions of the two pathways to polyploidy, the one-step ID$\rightarrow$CP transitions, and the two-step, ID$\rightarrow$CD$\rightarrow$CP transitions.
        Panel (a) shows the contributions when considering only transition rates among the states (ignoring the diversification rate parameters). 
        The one-step pathway dominates on short timescales and the two-step on long timescales.
        Panels (b) shows the contributions when including diversification of lineages in each state. 
        The one-step pathway, in which polyploidy breaks down SI, dominates over any timescale.
        Panels (c) and (d) plot the ratio of the pathway contributions in the upper panels, (a) and (b), respectively.
    }

    the one-step pathway, from ID to CP

    \label{figure:pathways}
\end{figure}

>>>>

When considering breeding system alone (I/C model, \cref{figure:netdivall}C), we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010}. %B: moved \cref{} earlier; avoids seeming related to \citep{}
When a hidden state is included (I/C+A/B model), the large net diversification difference persists for one of the hidden states but is removed for the other (\cref{figure:netdivall}D).
Thus, differences in net diversification are best explained by both breeding system and an unknown factor, similar to results found by \citet{freyman_2018}.
% The transition rate from SI to SC is $q_{IC}=0.3$ for both the I/C and the I/C+A/B models.
The statistical model comparison shows very strong support for including the hidden state (\cref{table:bayesfactors}).

@@

% E todo: could make this look a little less klunky
\begin{figure}
    \centering \includegraphics[width=0.9\textwidth]{pathways}
    \caption{
        Contributions of the two pathways to polyploidy.
        The one-step pathway is direct ID$\rightarrow$CP transitions.
        The two-step pathway consists of ID$\rightarrow$CD$\rightarrow$CP transitions.
        When considering only rates of transitions among the states (ignoring the diversification rate parameters), the one-step pathway dominates on short timescales and the two-step on long timescales (left panels).
        When also considering diversification within each state, the one-step pathway, in which polyploidization breaks down SI, dominates over any timescale (right panels).
        The top panels show the separate contributions of each pathway.
        The bottom panels show the proportional contribution of the one-step pathway (\ie one-step / [one-step + two-step]).
    }
    \label{figure:pathways}
\end{figure}
